\subsection{Connected Subspaces of the Real Line}

\begin{exercise}[ID=3.24.1]
  \begin{enumerate}[label={(\alph*)}, align=left, leftmargin=\parindent, listparindent=\parindent, labelwidth=0pt, itemindent=!]
    \item
      Show that no two of the spaces $(0, 1)$, $(0, 1]$, and $[0, 1]$ are homeomorphic.
    \item
      Suppose that there exist imbeddings $f: X \rightarrow Y$ and $g: Y \rightarrow X$.
      Show by means of an example that $X$ and $Y$ need not be homeomorphic.
    \item 
      Show that $\RR^n$ and $\RR$ are not homeomorphic if $n > 1$.
    \end{enumerate}
\end{exercise}
%
\begin{solution}
  \begin{enumerate}[label={(\alph*)}, align=left, leftmargin=\parindent, listparindent=\parindent, labelwidth=0pt, itemindent=!]
    \item
      Show that no two of the spaces $(0, 1)$, $(0, 1]$, and $[0, 1]$ are homeomorphic.
  \end{enumerate}
  %
  \begin{proof}
    Suppose by way of contradiction there is a homeomorphism
    %
    \begin{equation*}
      f: (0, 1] \rightarrow (0, 1).
    \end{equation*}
    %
    Then the map
    %
    \begin{align*}
      g: (0, 1) &\rightarrow (0, 1) \setminus f(\{1\}) \\
              x &\mapsto f(x)
    \end{align*}
    %
    is also a homeomorphism.
    But since $f(1) \in (0, 1)$ by hypothesis, $(0, 1) \setminus f(\{1\}) = (0, f(1)) \cup (f(1), 1)$ is disconnected.
    Since $(0, 1)$ is connected, its image under a continuous map must also be connected.
    This contradicts that $g$, and therefore $f$, are homeomorphisms.
    Thus, $(0, 1)$ and $(0, 1]$ are not homeomorphic.
    The proofs for the other spaces follow analogously.
  \end{proof}
  \bigskip

  \begin{enumerate}[label={(\alph*)}, align=left, leftmargin=\parindent, listparindent=\parindent, labelwidth=0pt, itemindent=!]
    \addtocounter{enumi}{1} 
    \item
      Suppose that there exist imbeddings $f: X \rightarrow Y$ and $g: Y \rightarrow X$.
      Show by means of an example that $X$ and $Y$ need not be homeomorphic.
  \end{enumerate}
  \begin{proof}
    We have seen in part (a) that the spaces $(0, 1)$ and $(0, 1]$ are not homeomorphic.
    Nevertheless, we can construct imbeddings between them.
    Consider the map
    %
    \begin{align*}
      f:  (0, 1]  &\rightarrow (0, 1) \\
                x & \mapsto x / 2.
    \end{align*}
    %
    Then the map $f': (0, 1] \rightarrow (0, 1/2]$ obtained by restricting the range of $f$ to its image set $f((0, 1])$, considered as a subspace of $(0, 1)$ is a homeomorphism.
    Thus, $f$ is an imbedding of $(0, 1]$ in $(0, 1)$.

    Consider now the map
    %
    \begin{equation*}
      g: (0, 1) \rightarrow (0, 1]
    \end{equation*}
    %
    given by the inclusion function.
    Then the map $g': (0, 1) \rightarrow (0, 1)$ obtained by restricting the range of $g$ to its image set $g((0, 1))$, considered as a subspace of $(0, 1]$ is just the identity map and, thus, a homeomorphism.
    Thus, $g$ is an imbedding of $(0, 1)$ in $(0, 1]$.
  \end{proof}
  \bigskip

  \begin{enumerate}[label={(\alph*)}, align=left, leftmargin=\parindent, listparindent=\parindent, labelwidth=0pt, itemindent=!]
    \addtocounter{enumi}{2} 
    \item 
      Show that $\RR^n$ and $\RR$ are not homeomorphic if $n > 1$.
  \end{enumerate}
  \begin{proof}
    Suppose by way of contradiction there is a homeomorphism
    %
    \begin{equation*}
      f: \RR^n \rightarrow \RR
    \end{equation*}
    %
    for some integer $n > 1$.
    Then the map
    %
    \begin{align*}
      g: \RR^n \setminus \{\mathbf{0}\} &\rightarrow \RR \setminus f(\{\mathbf{0}\}) \\
                                      x &\mapsto f(x)
    \end{align*}
    %
    is also a homeomorphism.
    But since $f(\mathbf{0}) \in \RR$ by hypothesis, $\RR \setminus f(\{\mathbf{0}\}) = (-\infty, f(\mathbf{0})) \cup (f(\mathbf{0}), \infty)$ is disconnected.
    Since we have seen previously that punctured euclidean space $\RR^n \setminus \{\mathbf{0}\}$ is connected for $n > 1$, its image under a continuous map must also be connected.
    This contradicts that $g$, and therefore $f$, are homeomorphisms.
    Thus, $\RR^n$ and $\RR$ are not homeomorphic if $n > 1$.
  \end{proof}
\end{solution}
\newpage

\begin{exercise}[ID=3.24.2]
  Let $f: S^1 \rightarrow \RR$ be a continuous map.
  Show there exists a point $x$ of $S^1$ such that $f(x) = f(-x)$.
\end{exercise}
%
\begin{solution}
  \begin{proof}
    Let $f: S^1 \rightarrow \RR$ be a continuous map.
    Then the map
    %
    \begin{align*}
      g: S^1  &\rightarrow \RR \\
            x &\mapsto f(x) - f(-x)
    \end{align*}
    %
    is also continuous.

    Assume by way of contradiction that for all $x \in S^1$, $f(x) \neq f(-x)$.
    Then $g(S^1) \subset \RR \setminus \{0\} = (-\infty, 0) \cup (0, \infty)$, which is disconnected.
    Since $g(x) = -g(-x)$, it must be that $g(S^1) \cap (-\infty, 0) \neq \emptyset$ and $g(S^1) \cap (0, \infty) \neq \emptyset$.
    But as $S^1$ is a connected space, this contradicts the fact that the image of $S^1$ under a continuous map is connected and, thus, must lie either entirely within $(-\infty, 0)$ or within $(0, \infty)$.
    Thus, if $f: S^1 \rightarrow \RR$ is a continuous map, then there exists a point $x$ of $S^1$ such that $f(x) = f(-x)$.
  \end{proof}
\end{solution}
\newpage

\begin{exercise}[ID=3.24.3]
  Let $f: X \rightarrow X$ be a continuous map.
  Show that if $X = [0, 1]$, there is a point $x$ such that $f(x) = x$.
  What happens if $X$ equals $[0, 1)$ or $(0, 1)$?
\end{exercise}
%
\begin{solution}
  \begin{proof}
    Let $f: [0, 1] \rightarrow [0, 1]$ be a continuous map.
    Then the map
    %
    \begin{align*}
      g: [0, 1] &\rightarrow [-1, 1] \\
              x &\mapsto f(x) - x
    \end{align*}
    %
    is also continuous.
    Since $g(0) = f(0) \geq 0$ and $g(1) = f(1) - 1 \leq 0$, by the intermediate value theorem there exists an $x \in [0, 1]$ satisfying $g(x) = 0$ and, thus, $f(x) = x$.

    We now consider what happens when $X = [0, 1)$ or $X = (0, 1)$.
    Consider the map
    %
    \begin{align*}
      f: X  &\rightarrow X \\
         x  &\mapsto \frac{x + 1}{2}.
    \end{align*}
    %
    The only solution to $f(x) = x$ in this case would be $x = 1$.
    However, $1 \not\in X$ for either case.
    Thus, for $X = [0, 1)$ or $X = (0, 1)$ a continous map $f: X \rightarrow X$ need not have a fixed point.
  \end{proof}
\end{solution}
\newpage

\begin{exercise}[ID=3.24.4]
  Let $X$ be an ordered set in the order topology.
  Show that if $X$ is connected, then $X$ is a linear continuum.
\end{exercise}
%
\begin{solution}
  \begin{proof}
    Let $X$ be an ordered set in the order topology which is connected.
    Suppose by way of contradiction that $X$ is not a linear continuum.
    We consider two possibilities.

    Suppose first that $X$ does not satisfy the least upper bound property.
    Then there exists some nonempty subset $A$ of $X$ which is bounded above but for which there exists no least upper bound in $X$.
    Let $B = \{ b \in X \mid a \leq b, \forall a \in A \}$ be the set of upper bounds of $A$.
    Since $A$ has no least upper bound, $B$ does not have a smallest element.
    Thus, defining open sets
    %
    \begin{equation}
      U = \bigcup_{a \in A} (-\infty, a) \; \text{ and }\; V = \bigcup_{b \in B} (b, \infty),
    \end{equation}
    %
    we have that $X = U \cup V$ is a separation of $X$, contradicting our assumption that $X$ is connected.

    Suppose instead there exist $x, y \in X$ with $x < y$ such that for any $z \in X$, it is not the case that $x < z < y$.
    Then we have that $X = (-\infty, y) \cup (x, \infty)$ is a separation of $X$, contradicting our assumption that $X$ is connected.
  \end{proof}
\end{solution}
\newpage

\begin{exercise}[ID=3.24.6]
  Show that if $X$ is a well-ordered set, then $X \times [0, 1)$ in the dictionary order is a linear continuum.
\end{exercise}
%
\begin{solution}
  \begin{proof}
    Let $X$ be a well-ordered set and let $A \subset X \times [0, 1)$ be a nonempty subset of $X \times [0, 1)$ in the dictionary order which is bounded above.

    \subsubsection*{The dictionary order satisfies the least upper bound property}
    %
    By hypothesis there exists some upper bound $(x, u) \in X \times [0, 1)$ of $A$.
    It must then be the case that $\pi_1(A) \subset X$ is bounded from above by $x$, where $\pi_1$ is the projection map from $A$ to the first factor.
    Since $X$ is well-ordered by hypothesis, $\pi_1(A)$ must possess a least upper bound $z \in X$.
    We consider the two cases $\pi_1\inv(\{z\}) = \emptyset$ and $\pi_1\inv(\{z\}) \neq \emptyset$ and show that in each case there exists a least upper bound for $A$.
    
    Suppose $\pi_1\inv(\{z\}) = \emptyset$.
    Then $(z, 0)$ is an upper bound for $A$.
    Let $(x, u)$ be some upper bound for $A$.
    Since $z$ is the least upper bound for $\pi_1(A)$, we have that $z \leq x$.
    Furthermore, since $0 \leq u$ we have that $(z, 0) \leq (x, u)$ and so $(z, 0)$ is the least upper bound for $A$.

    Suppose instead that $\pi_1\inv(\{z\}) \neq \emptyset$.
    Then $u$ must bound $\pi_2(\pi_1\inv(\{z\})) \subset [0, 1)$ from above, where $\pi_2$ is the projection map from $A$ to the second factor.
    Since $[0, 1)$ is a linear continuum it possesses the least upper bound property.
    It follows that $\pi_2(\pi_1\inv(\{z\}))$ has a least upper bound $w \in [0, 1)$.

    We now show that $(z, w) \in X \times [0, 1)$ is the least upper bound for $A$.
    Let $(y, v) \in A$.
    Since $z$ is the least upper bound for $\pi_1(A)$, it must be that $y \leq z$.
    If $y < z$, then $(y, v) < (z, w)$.
    If instead $y = z$, we note that since $w$ is the least upper bound for $\pi_2(A)$, it must be that $v \leq w$.
    Thus, for arbitrary $(y, v) \in X \times [0, 1)$, we see that $(y, v) \leq (z, w)$, from which it follows that $(z, w)$ is an upper bound for $A$.

    Now let $(x, u)$ be an upper bound for $A$.
    Then for all $(y, v) \in A$, either $y < x$ or $y = x$ and $v \leq u$.
    Suppose first that $y < x$.
    Since $z$ is the least upper bound for $\pi_1(A)$, then $z \leq x$.
    If $z < x$, then $(z, w) < (x, u)$.
    If instead $z = x$, we note that $w$ is the least upper bound for $\pi_2(A)$ and so $w \leq u$.
    Thus, $(z, w) \leq (x, u)$.
    Suppose instead that $y = x$. Since $z$ is the least upper bound for $\pi_1(A)$, then $z = x$.
    As above, since $w$ is the least upper bound for $\pi_2(A)$, we have that $w \leq u$.
    Thus, $(z, w) \leq (x, u)$.
    It follows that $(z, w)$ furnishes a least upper bound for the arbitrary nonempty, bounded from above subset $A$ of $X \times [0, 1)$ in the dictionary order.

    \subsubsection*{If $(x, u) < (y, v)$, there exists $(z, w)$ such that $(x, u) < (z, w) < (y, v)$}
    %
    Let $(4x, u), (y, v) \in X \times [0, 1)$ with $(x, u) < (y, v)$.
    Suppose $x < y$.
    Since $[0, 1)$ is a linear continuum, we can always find $w \in [0, 1)$ such that $u < w$.
    Choosing $z = x$, we have $(x, u) < (z, w) < (y, v)$.

    Suppose instead that $x = y$ and $u < v$.
    Again, as $[0, 1)$ is a linear continuum, we can find $w \in [0, 1)$ such that $u < w < v$.
    Choosing $z = x$, we have $(x, u) < (z, w) < (y, v)$.
    Thus, we see that $X \times [0, 1)$ in the dictionary order is a linear continuum.
  \end{proof}
\end{solution}
\newpage

\begin{exercise}[ID=3.24.7]
  \begin{enumerate}[label={(\alph*)}, align=left, leftmargin=\parindent, listparindent=\parindent, labelwidth=0pt, itemindent=!]
    \item
      Let $X$ and $Y$ be ordered sets in the order topology.
      Show that if $f: X \rightarrow Y$ is order preserving and surjective, then $f$ is a homeomorphism.
    \item
      Let $X = Y = \overline{\RR}_+$.
      Given a positive integer $n$, show that the function $f(x) = x^n$ is order preserving and surjective.
      Conclude that its inverse, the $n$\textit{th root function}, is continous.
    \item 
      Let $X$ be the subspace $(-\infty, -1) \cup [0, \infty)$ of $\RR$.
      Show that the function $f: X \rightarrow \RR$ defined by setting $f(x) = x + 1$ if $x < -1$, and $f(x) = x$ if $x \geq 0$, is order preserving and surjective.
      Is $f$ a homeomorphism?
      Compare with (a).
    \end{enumerate}
\end{exercise}
%
\begin{solution}
  \begin{enumerate}[label={(\alph*)}, align=left, leftmargin=\parindent, listparindent=\parindent, labelwidth=0pt, itemindent=!]
    \item
      Let $X$ and $Y$ be ordered sets in the order topology.
      Show that if $f: X \rightarrow Y$ is order preserving and surjective, then $f$ is a homeomorphism.
  \end{enumerate}
  \begin{proof}
    Let $f: X \rightarrow Y$ be order preserving and surjective.
    We begin by showing that $f$ must be bijective with order preserving inverse.
    Given $u, v \in X$, if $u \neq v$ then either $u < v$ or $v < u$, since $X$ is an ordered set.
    Without loss of generality, suppose that $u < v$.
    Since $f$ is order preserving, we have that $f(u) < f(v)$ so that $f(u) \neq f(v)$.
    Thus, $f$ injective in addition to being surjective and is, therefore, a bijection.

    Let $a, b \in Y$ and let $u = f\inv(a)$ and $v = f\inv(b)$.
    Suppose by way of contradiction that $f\inv$ is not order preserving.
    Since $f$ is bijective, $u = v$ if and only if $a = b$.
    Suppose that $a < b$ so that $u \neq v$.
    Since we assume that $f\inv$ is not order preserving, it is possible that $v < u$.
    As $f$ \textit{is} order preserving, this would imply that $b = f(v) < f(u) = a$, contradicting our assumption that $a < b$.
    Thus, $f\inv: Y \rightarrow X$ is order preserving.

    We now show that continuity of $f$ follows directly from it being order preserving and bijective.
    Under the order topology, basic open sets in $Y$ are either of the form (i) open intervals $(a, b)$ in $Y$, (ii) intervals of the form $[a_0, b)$, where $a_0$ is the smallest element (if any) in $Y$, (iii) intervals of the form $(a, b_0]$, where $b_0$ is the largest element (if any) of $Y$.
    Since $f\inv$ is order preserving, we thus consider sets in $X$ of the form (i) $f\inv((a, b)) = (f\inv(a), f\inv(b))$, (ii) $f\inv([a_0, b)) = [f\inv(a_0), f\inv(b))$, (iii) $f\inv((a, b_0]) = (f\inv(a), f\inv(b_0)]$.
    As these are nothing more than the basic open sets in $X$ under the order topology, we have that $f$ is continuous.

    Since $f\inv$ is also order preserving and bijective, it must also be continuous.
    Thus, $f: X \rightarrow Y$ is a homeomorphism.
  \end{proof}
  \newline

  %
  \begin{enumerate}[label={(\alph*)}, align=left, leftmargin=\parindent, listparindent=\parindent, labelwidth=0pt, itemindent=!]
    \addtocounter{enumi}{1} 
    \item
      Let $X = Y = \overline{\RR}_+$.
      Given a positive integer $n$, show that the function $f(x) = x^n$ is order preserving and surjective.
      Conclude that its inverse, the $n$\textit{th root function}, is continous.
  \end{enumerate}
  %
  \begin{proof}~

    \subsubsection*{$x^n$ is order preserving}
    %
    Let $x, y \in \overline{\RR}_+$ with $x < y$ and define $\delta = y - x > 0$.
    Then
    %
    \begin{equation*}
      y^n = (x + \delta)^n \geq x + n \delta
    \end{equation*}
    %
    and, similarly,
    %
    \begin{equation*}
      x^n = (y - \delta)^n \geq y - n \delta.
    \end{equation*}
    %
    Their difference, therefore, satisfies
    %
    \begin{equation*}
      y^n - x^n \geq x - y + 2 n \delta = (2n - 1) \delta \geq \delta > 0.
    \end{equation*}
    %
    It follows that $x^n < y^n$ and, thus, $x^n$ is order preserving.
    \bigskip

    %
    \subsubsection*{$x^n$ is surjective}
    %

  \end{proof}
\end{solution}
\newpage

